### 2020-11-06 written/SC_model/SC_model.tex
sc update tetx

\section{Identifying neural mechanisms of flexible task switching} \label{results_SC}
In a rapid task switching experiment \cite{duan2015requirement}, rats were explicitly cued on each trial to either orient towards a visual stimulus in the Pro (P) task or orient away from a visual stimulus in the Anti (A) task (Fig. \ref{fig:SC}a). 
Neural recordings in the midbrain superior colliculus (SC) exhibited two populations of neurons that simultaneously represented both task context (Pro or Anti) and motor response (contralateral or ipsilateral to the recorded side): the Pro/Contra and Anti/Ipsi neurons \cite{duan2018collicular}.
Duan et al. proposed a model of SC that, like the V1 model analyzed in the previous section, is a four-population dynamical system.  
We analyzed this model, where the neuron-type populations are functionally-defined as the Pro- and Anti-populations in each hemisphere (left (L) and right (R)), their connectivity is parameterized geometrically  (Fig. \ref{fig:SC}B).
The input-output function of this model is chosen such that the population responses $x = [x_{LP}, x_{LA}, x_{RP}, x_{RA}]^\top$ are bounded from 0 to 1 giving rise to high (1) or low (0) responses at the end of the trial:
\begin{equation}
x_\alpha =\left(\frac{1}{2}\tanh\left(\frac{u_\alpha - \epsilon}{\zeta}\right)+ \frac{1}{2} \right)
\end{equation}
where $\epsilon = 0.05$ and $\zeta = 0.5$.  
The dynamics evolve with timescale $\tau=0.09$ via an internal variable $u$ governed by connectivity weights $W$
\begin{equation}
\tau \frac{du}{dt} = -u + Wx + h + \sigma dB
\end{equation}
with gaussian noise of variance $\sigma^2$ = 1.
The input $h$ is comprised of a cue-dependent input to the Pro or Anti populations, a stimulus orientation input to either the Left or Right populations, and a choice-period input to the entire network (see Section \ref{methods_SC}).
Here, we use EPI to determine the changes in network connectivity $z = [ sW_P, sW_A, vW_{PA}, vW_{AP}, dW_{PA}, dW_{AP}, hW_P, hW_A]$ resulting in greater levels of rapid task switching accuracy.

@@

To quantify the emergent property of rapid task switching at various levels of accuracy, we considered the requirements of this model in this behavioral paradigm.
At the end of successful trials, the response of the Pro population in the hemisphere of the correct choice must have a value near 1, while the Pro population in the opposite hemisphere must have a value near 0.
Constraining a population response $x_\alpha \in \left[0,1\right]$ to be either 0 or 1 can be achieved by requiring that it has Bernoulli variance (see Section \ref{methods_SC}).
Thus, we can formulate rapid task switching at a level of accuracy $p \in \left[0, 1\right]$ in both tasks in terms of the average steady response of the Pro population $\hat{p}$ of the correct choice,  the error in Bernoulli variance of that Pro neuron $\sigma^2_{\text{err}}$, and the average difference in Pro neuron responses $d$ in both Pro and Anti trials:
\begin{equation}
\mathcal{B}(p) ~~\triangleq~~ \mathbb{E}\begin{bmatrix} \hat{p}_P \\ \hat{p}_A \\ (\hat{p}_P-p)^2 \\ (\hat{p}_A - p)^2 \\ \sigma^2_{P,err} \\ \sigma^2_{A,err} \\ d_P \\ d_A \end{bmatrix} = \begin{bmatrix} p \\ p \\ 0.15^2 \\ 0.15^2 \\ 0 \\ 0 \\ 1 \\ 1 \end{bmatrix}.
\end{equation}
Thus, $\mathcal{B}(p)$ denotes Bernoulli, winner-take-all responses between Pro neurons in a model executing rapid task switching near accuracy level $p$.

>>>>

\section{Identifying neural mechanisms of flexible task switching} \label{results_SC}
In a rapid task switching experiment \cite{duan2015requirement}, rats were explicitly cued on each trial to either orient towards a visual stimulus in the Pro (P) task or orient away from a visual stimulus in the Anti (A) task (Fig. \ref{fig:SC}a). 
Neural recordings in the midbrain superior colliculus (SC) exhibited two populations of neurons that simultaneously represented both task context (Pro or Anti) and motor response (contralateral or ipsilateral to the recorded side): the Pro/Contra and Anti/Ipsi neurons \cite{duan2018collicular}.
Duan et al. proposed a model of SC that, like the V1 model analyzed in the previous section, is a four-population dynamical system.  
We analyzed this model, where the neuron-type populations are functionally-defined as the Pro- and Anti-populations in each hemisphere (left (L) and right (R)), their connectivity is parameterized geometrically  (Fig. \ref{fig:SC}B).
The input-output function of this model is chosen such that the population responses $x = [x_{LP}, x_{LA}, x_{RP}, x_{RA}]^\top$ are bounded from 0 to 1 giving rise to high (1) or low (0) responses at the end of the trial:
\begin{equation}
x_\alpha =\left(\frac{1}{2}\tanh\left(\frac{u_\alpha - \epsilon}{\zeta}\right)+ \frac{1}{2} \right)
\end{equation}
where $\epsilon = 0.05$ and $\zeta = 0.5$.  
The dynamics evolve with timescale $\tau=0.09$ via an internal variable $u$ governed by connectivity weights $W$
\begin{equation}
\tau \frac{du}{dt} = -u + Wx + h + \sigma dB
\end{equation}
with gaussian noise of variance $\sigma^2$ = 0.2.
The input $h$ is comprised of a cue-dependent input to the Pro or Anti populations, a stimulus orientation input to either the Left or Right populations, and a choice-period input to the entire network (see Section \ref{methods_SC}).
Here, we use EPI to determine the changes in network connectivity $z = [sW, vW, dW, hW]^{\top}$ resulting in greater levels of rapid task switching accuracy.

@@

To quantify the emergent property of rapid task switching , we considered the requirements of this model in this behavioral paradigm.
At the end of successful trials, the response of the Pro population in the hemisphere of the correct choice must be greater than the Pro population in the opposite hemisphere.
Thus, we can formulate rapid task switching accuracy as the average number of successful trials over gaussian noise.
\begin{equation}
\mathcal{B}(p) ~~\triangleq~~ \mathbb{E}\begin{bmatrix} \hat{p}_P \\ \hat{p}_A \\ (\hat{p}_P-p)^2 \\ (\hat{p}_A - p)^2 \\ \sigma^2_{P,err} \\ \sigma^2_{A,err} \\ d_P \\ d_A \end{bmatrix} = \begin{bmatrix} p \\ p \\ 0.15^2 \\ 0.15^2 \\ 0 \\ 0 \\ 1 \\ 1 \end{bmatrix}.
\end{equation}
Thus, $\mathcal{B}(p)$ denotes Bernoulli, winner-take-all responses between Pro neurons in a model executing rapid task switching near accuracy level $p$.
